---
title: "When 46K Optimism Users Use Your App For No Reason"
author: "Graham Onders"
date: "`r Sys.Date()`"
output:
  html_document:
    css: "styles.css"
    includes:
      in_header: header.html
    code_folding: hide
    toc: true
    toc_float: true
editor_options: 
  chunk_output_type: console
---

FlipsideCrypto's Research is open source. Check out all the code for this report [here](https://github.com/fsc-data-science/Op-Attestation-Research) on github.

```{r, warning = FALSE, message = FALSE}
# Libraries
library(shroomDK)
library(reactable)
library(ggplot2)
library(plotly)
library(lubridate)
library(dplyr)
```

# Intro

Late in 2022, Optimism Foundation approached Flipside, requesting that Flipside contribute to their new [Attestation Station](https://community.optimism.io/docs/governance/attestation-station/). The idea being that users should be able to attest to their on or off chain behaviors to an on-chain contract in a peer-to-peer manner. This will help addresses to attest to their actions, building an on-chain reputation or identity!

In response to this request, Flipside created the [Optimist Score](https://science.flipsidecrypto.xyz/optimist/) as a way to attest to an address' specific on-chain behaviors. With minimal marketing for this tool, Flipside recieved over 45,000 attestations. 

Many of these attestations can be attributed to hype around an Optimism airdrop, that doesn't exist (yet...). However, even the slightest non-hint of an airdrop will get tens of thousands of people to do things on chain. 
How can this power be used to benefit a protocol?

Lets take a look at Flipside's Optimism attestion score and see what type of addresses are attesting on chain!

```{r, warning = FALSE, message = FALSE}

daily_query <- {
  "
  with base as (
select *,
regexp_substr_all(SUBSTR(DATA, 3, len(DATA)), '.{64}') AS segmented_data
from optimism.core.fact_event_logs
where block_timestamp > '2022-12-14'
and block_timestamp < '2023-01-31'
and contract_address = '0xee36eaad94d1cc1d0eccadb55c38bffb6be06c77' 
and topics[0]::string = '0x28710dfecab43d1e29e02aa56b2e1e610c0bae19135c9cf7a83a1adb6df96d85'
),
decoded_data as (
select
block_number,
block_timestamp,
tx_hash,
origin_from_address,
origin_to_address,
event_index,
CONCAT('0x', SUBSTR(topics [1] :: STRING, 27, 40)) AS creator,
CONCAT('0x', SUBSTR(topics [2] :: STRING, 27, 40)) AS about,
replace(topics [3] :: STRING,'0x','') as key,
try_hex_decode_string(key::string) as decoded_key,
substr(data::string,131,(ethereum.public.udf_hex_to_int(segmented_data[1]::string) * 2)) as val,
try_hex_decode_string(val::string) as val_text
from base
)

select
  date(block_timestamp) as date,
  origin_to_address,
  case when origin_to_address = '0xd870a73a32d0b8c34ccf1e6098e9a26977cb605b' then 'Flipside' 
  when origin_to_address = '0xd34a8775d06d41b36054d59ef2d09a79b7aa1fa2' then 'Clique'
  else 'Other' end as origin_to_labeled,
  count(distinct tx_hash) as num_attestations,
  count(distinct about) as num_unique_attestation_addresses,
  num_attestations - num_unique_attestation_addresses as num_duplicate_attestations
from decoded_data
group by 1,2
  "
}

# not run 
# daily_attestations <- auto_paginate_query(daily_query, api_key = readLines("api_key.txt"))

# provided pre-ran 
daily_attestations <- read.csv("daily_attestations_data.csv",
                               colClasses=c("ORIGIN_TO_ADDRESS"="character"))
colnames(daily_attestations) <- tolower(colnames(daily_attestations))
daily_attestations$date <- as.Date(daily_attestations$date, format = "%m/%d/%Y")

daily_attestations <- daily_attestations[order(daily_attestations$date), ]

```

# Optimist Users

```{r, warning = FALSE, message = FALSE}

flipside <- daily_attestations %>% 
  filter(origin_to_address == '0xd870a73a32d0b8c34ccf1e6098e9a26977cb605b')

```

Looking at all Optimist attestors between December 15, 2022 (date of launch) and January 30, 2023 (date of analysis), there have been `r format(sum(flipside$num_attestations), big.mark=",")` attestations!


```{r, warning = FALSE, message = FALSE}
plot_ly(data = flipside, 
        x = ~date, 
        y = ~num_attestations,
        type = "scatter", 
        mode = "lines",
        line = list(color = '#FF5517')) %>% 
  layout(
    title = list(text = "Number of Attestations Over Time", y = 0.975),
    xaxis = list(title = "Date"),
    yaxis = list(title = "Number Attestations")
  )

```

What caused all of these users to want to use our attestation tool? Lets dive into what drove users! 

## How is Flipside's tool different than others

When we look at Flipside's attestation tool, there are a few separating factors that set us apart from other Optimism attestation tools: 

1. Flipside's attestation tool was the first (and only for awhile) with the ability to put your score on-chain. Flipside built a smart contract that was able to interact with Optimism's attestation contract, allowing for users to attest to their score on-chain!
2. Our attestation tool supported wallet connect. This means that the score we were giving users was provable and had metrics based on that address's on chain activity. It wasn't just a random number.
3. Flipside has some experience with picking scoring users based on on-chain activities with our [hop airdrop review](https://science.flipsidecrypto.xyz/hopdrop/hopdrop.html), [eth timecard](https://science.flipsidecrypto.xyz/eth-timecard/), [lunatics score](https://science.flipsidecrypto.xyz/lunatics/), [terrascored](https://science.flipsidecrypto.xyz/terrascored/) and others. 

## What kind of marketing did Flipside do?

Building this tool, we didn't have very many expectations. It was more of a prototype for an on-chain scoring method. We were flexing our smart contract development skills and wanted to parter with Optimism in a fun way. The only real marketing that this app received was through Optimism's weekly [twitter thread](https://twitter.com/optimismFND/status/1603437484603490305) where their Attestation Station was announced and Flipside received a nice shout out for our new tool! 

Our attestation tool also was added to their [docs](https://community.optimism.io/docs/governance/attestation-station/#general-faq) as one of the products that is built on the Attestation Station. 


## What's up with the spikes in activity?

If you look at the attestation activity graph above, you may be wondering - what caused the three very clear spikes in activity? It couldn't all be from the initial twitter thread?

The first spike on December 16th was, in fact, due to the initial Optimism announcement on [Twitter](https://twitter.com/optimismFND/status/1603437484603490305). Users were excited about the new product, and we were really the only product that supported on chain attestations!

However, excitement dwindled and attestations tapered off until early January when a new attestation tool was created. 

On January 6th, Clique created their own twitter/social [attestation tool](https://clique.social/attestor/opattestor). This came in tandem with another Optimism announcement [via twitter](https://twitter.com/optimismFND/status/1611436116925681688). 

We can see our attestations grow along side of Clique's. 

In fact we can see the correlation if we overlay the activity of Clique with Flipside!

```{r, warning = FALSE, message = FALSE}
plot_ly(data = daily_attestations, 
        x = ~date, 
        y = ~num_attestations,
        type = "scatter", 
        color = ~origin_to_labeled,
        mode = "lines") %>% 
  layout(
    title = list(text = "Number of Attestations Over Time", y = 0.975),
    xaxis = list(title = "Date"),
    yaxis = list(title = "Number Attestations")
  )
```


We can see users of the flipside attestation tool spike alongside the clique attestations! 


The third spike can be attributed to airdrop hype. There was a lot of speculuation for a second Optimism airdrop and large twitter accounts such as [airdrop inspector](https://twitter.com/airdropinspect) and [AirdropDetective](https://twitter.com/AirdropDet) announced that utilization of the attestation station would lead to a larger airdrop.


# What Kind of Users Attributed to Flipsides Attestation Tool

Since our attestation tool is based on on-chain activity and allows for the user to attest to their score on-chain, we can take a look at the type of wallets that attested and their individual behaviors!

## Duplicate addresses

```{r, warning = FALSE, message = FALSE}

full_attestation_table_query <- {
  "
with base as (
select *,
regexp_substr_all(SUBSTR(DATA, 3, len(DATA)), '.{64}') AS segmented_data
from optimism.core.fact_event_logs
where block_timestamp > '2022-12-14'
and block_timestamp < '2023-01-31'
and contract_address = '0xee36eaad94d1cc1d0eccadb55c38bffb6be06c77' 
and topics[0]::string = '0x28710dfecab43d1e29e02aa56b2e1e610c0bae19135c9cf7a83a1adb6df96d85'
),
decoded_data as (
select
block_number,
block_timestamp,
tx_hash,
origin_from_address,
origin_to_address,
event_index,
CONCAT('0x', SUBSTR(topics [1] :: STRING, 27, 40)) AS creator,
CONCAT('0x', SUBSTR(topics [2] :: STRING, 27, 40)) AS about,
replace(topics [3] :: STRING,'0x','') as key,
try_hex_decode_string(key::string) as decoded_key,
substr(data::string,131,(ethereum.public.udf_hex_to_int(segmented_data[1]::string) * 2)) as val,
try_hex_decode_string(val::string) as val_text
from base
)

select
  origin_to_address,
  decoded_key as attestation_address_name,
  count(*) as num_attestations,
  count(distinct about) as num_unique_attestation_addresses,
  num_attestations - num_unique_attestation_addresses as num_duplicate_attestations
from decoded_data
-- Flipside & Clique only 
where origin_to_address in ('0xd870a73a32d0b8c34ccf1e6098e9a26977cb605b', '0xd34a8775d06d41b36054d59ef2d09a79b7aa1fa2')
group by 1,2

order by 3 desc
  "
}


# not run 
# full_attestation_table <- auto_paginate_query(full_attestation_table_query, api_key = readLines("api_key.txt"))

# provided pre-ran 
full_attestation_table <- read.csv("full_attestation_table_data.csv",
                               colClasses=c("ORIGIN_TO_ADDRESS"="character"))
colnames(full_attestation_table) <- tolower(colnames(full_attestation_table))

```

```{r, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
reactable(full_attestation_table)
```


When looking at the table above we can see that Flipside did in fact receive quite a few duplicate attestations (almost 9K of our 45K attesations: ~20% of Total), while Clique only received about 500. 

Over time, we can see how duplicates change over time. There isn't any significant change to duplicate submissions. Fairly consistent at about 20%, which is good - demonstrating consistent usage behaviors over time!

```{r, warning = FALSE, message = FALSE}

duplicates_overtime_query <- {
  "
with base as (
select *,
regexp_substr_all(SUBSTR(DATA, 3, len(DATA)), '.{64}') AS segmented_data
from optimism.core.fact_event_logs
where block_timestamp > '2022-12-14'
and block_timestamp < '2023-01-31'
and contract_address = '0xee36eaad94d1cc1d0eccadb55c38bffb6be06c77' 
and topics[0]::string = '0x28710dfecab43d1e29e02aa56b2e1e610c0bae19135c9cf7a83a1adb6df96d85'
),
decoded_data as (
select
block_number,
block_timestamp,
tx_hash,
origin_from_address,
origin_to_address,
event_index,
CONCAT('0x', SUBSTR(topics [1] :: STRING, 27, 40)) AS creator,
CONCAT('0x', SUBSTR(topics [2] :: STRING, 27, 40)) AS about,
replace(topics [3] :: STRING,'0x','') as key,
try_hex_decode_string(key::string) as decoded_key,
substr(data::string,131,(ethereum.public.udf_hex_to_int(segmented_data[1]::string) * 2)) as val,
try_hex_decode_string(val::string) as val_text
from base
),

base_duplicates as (
  select
  distinct 
  block_timestamp,
  about as address,
  origin_to_address,
  val,
  row_number() over (partition by about,origin_to_address order by block_timestamp asc) as attestation_number,
  lag(block_timestamp,1) over (partition by about,origin_to_address order by block_timestamp asc) as date_diff
from decoded_data
where origin_to_address in ('0xd870a73a32d0b8c34ccf1e6098e9a26977cb605b')
)
select distinct block_timestamp,
address,
origin_to_address,
val,
attestation_number,
date_diff,
case when attestation_number = 1 then 'first_attestation'
when attestation_number > 1 then 'duplicate_attestation'
end as attestation_type,
datediff(minute,date_diff,block_timestamp) as time_between_attests,
date(block_timestamp) as dates,
1 as temp_val
from base_duplicates
order by 2,5 asc
  "
}

# not run 
# duplicates_overtime_table <- auto_paginate_query(duplicates_overtime_query, api_key = readLines("api_key.txt"))

# provided pre-ran 
duplicates_overtime_table <- read.csv("duplicates_over_time_data.csv",
                               colClasses=c("ORIGIN_TO_ADDRESS"="character", 'ADDRESS' = 'character'))
colnames(duplicates_overtime_table) <- tolower(colnames(duplicates_overtime_table))


```



```{r, warning = FALSE, message = FALSE}

duplicates_overtime_table_grouped <- duplicates_overtime_table %>%
  group_by(dates, attestation_type) %>%
  summarise(count = n_distinct(address)) %>% 
  arrange(dates)


plot_ly(data = duplicates_overtime_table_grouped, 
        x = ~dates, 
        y = ~count,
        split = ~attestation_type,
        type = "bar") %>% 
  layout(
    title = list(text = "Duplicate Attestation Percent Over Time", y = 0.99),
    xaxis = list(title = "Date"),
    yaxis = list(title = "% Attestations"),
    barmode = 'stack',
    barnorm = 'percent'
  )
```


But is this a bad thing? Not necessarily, our Optimism attestation tool is designed to give a higher score if a user has done specific things on chain. This would incentivize users to do more on chain and return to the tool, attesting to a higher score than previously!

Let's take a look at some of these usage trends!

## Retattestation

```{r, warning = FALSE, message = FALSE}

reattestation_query <- {
  "
with base as (
select *,
regexp_substr_all(SUBSTR(DATA, 3, len(DATA)), '.{64}') AS segmented_data
from optimism.core.fact_event_logs
where block_timestamp > '2022-12-14'
and block_timestamp < '2023-01-31'
and contract_address = '0xee36eaad94d1cc1d0eccadb55c38bffb6be06c77' 
and topics[0]::string = '0x28710dfecab43d1e29e02aa56b2e1e610c0bae19135c9cf7a83a1adb6df96d85'
),
decoded_data as (
select
block_number,
block_timestamp,
tx_hash,
origin_from_address,
origin_to_address,
event_index,
CONCAT('0x', SUBSTR(topics [1] :: STRING, 27, 40)) AS creator,
CONCAT('0x', SUBSTR(topics [2] :: STRING, 27, 40)) AS about,
replace(topics [3] :: STRING,'0x','') as key,
try_hex_decode_string(key::string) as decoded_key,
substr(data::string,131,(ethereum.public.udf_hex_to_int(segmented_data[1]::string) * 2)) as val,
try_hex_decode_string(val::string) as val_text
from base
),
base_duplicates as (
  select
  distinct 
  block_timestamp,
  about as address,
  origin_to_address,
  val,
  row_number() over (partition by about,origin_to_address order by block_timestamp asc) as attestation_number,
  lag(block_timestamp,1) over (partition by about,origin_to_address order by block_timestamp asc) as date_diff,
  lag(val,1) over (partition by about,origin_to_address order by block_timestamp asc) as val_diff
from decoded_data
-- Flipside 
where origin_to_address in ('0xd870a73a32d0b8c34ccf1e6098e9a26977cb605b')
)
select 
distinct
attestation_number,
count(address) as number_of_addresses,
avg(datediff(minute,date_diff,block_timestamp)) as avg_time_between_attests,
median(datediff(minute,date_diff,block_timestamp)) as med_time_between_attests,
avg(val-val_diff) as avg_diff_in_scores,
median(val-val_diff) as med_diff_in_scores
from base_duplicates
group by 1
order by 1 asc
  "
}

# not run 
# reattestation_table <- auto_paginate_query(reattestation_query, api_key = readLines("api_key.txt"))

# provided pre-ran 
reattestation_table <- read.csv("reattestation_table_data.csv")
colnames(reattestation_table) <- tolower(colnames(reattestation_table))

```

```{r, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
reactable(reattestation_table)
```

If we look at reattestations over time, we see that, on average, people who come back to reattest get a higher score by .2 points! this is an encouraging finding because, while there are people who are spamming/botting the attestation, users were incentivized to return to the app and reattest with a higher score after using Optimism in a new way!

This finding is even further emphasized if we split out the spammers/bots from the non spammers/bots

```{r, warning = FALSE, message = FALSE}

reattestation_breakout_query <- {
  "
with base as (
select *,
regexp_substr_all(SUBSTR(DATA, 3, len(DATA)), '.{64}') AS segmented_data
from optimism.core.fact_event_logs
where block_timestamp > '2022-12-14'
and block_timestamp < '2023-01-31'
and contract_address = '0xee36eaad94d1cc1d0eccadb55c38bffb6be06c77' 
and topics[0]::string = '0x28710dfecab43d1e29e02aa56b2e1e610c0bae19135c9cf7a83a1adb6df96d85'
),
decoded_data as (
select
block_number,
block_timestamp,
tx_hash,
origin_from_address,
origin_to_address,
event_index,
CONCAT('0x', SUBSTR(topics [1] :: STRING, 27, 40)) AS creator,
CONCAT('0x', SUBSTR(topics [2] :: STRING, 27, 40)) AS about,
replace(topics [3] :: STRING,'0x','') as key,
try_hex_decode_string(key::string) as decoded_key,
substr(data::string,131,(ethereum.public.udf_hex_to_int(segmented_data[1]::string) * 2)) as val,
try_hex_decode_string(val::string) as val_text
from base
),
base_duplicates as (
  select
  distinct 
  block_timestamp,
  about as address,
  origin_to_address,
  val,
  row_number() over (partition by about,origin_to_address order by block_timestamp asc) as attestation_number,
  lag(block_timestamp,1) over (partition by about,origin_to_address order by block_timestamp asc) as date_diff,
  lag(val,1) over (partition by about,origin_to_address order by block_timestamp asc) as val_diff
from decoded_data
where origin_to_address in ('0xd870a73a32d0b8c34ccf1e6098e9a26977cb605b')
)
select 
distinct
case when datediff(minute,date_diff,block_timestamp) < 720 then 'Quick Attest'
  when datediff(minute,date_diff,block_timestamp) >= 720 then 'Patient Attest'
  else 'First Attestation'
end as attestation_type,
attestation_number,
count(address) as number_of_addresses,
avg(datediff(minute,date_diff,block_timestamp)) as avg_time_between_attests,
median(datediff(minute,date_diff,block_timestamp)) as med_time_between_attests,
avg(val-val_diff) as avg_diff_in_scores,
median(val-val_diff) as med_diff_in_scores
from base_duplicates
group by 1,2
order by 1,2 asc

  "
}

# not run 
# reattestation_breakout_table <- auto_paginate_query(reattestation_breakout_query, api_key = readLines("api_key.txt"))


# provided pre-ran 
reattestation_breakout_table <- read.csv("reattestation_table_breakout_data.csv")
colnames(reattestation_breakout_table) <- tolower(colnames(reattestation_breakout_table))

```

```{r, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
reactable(reattestation_breakout_table)
```
In this table, we define a patient attestor as someone who waited at least 12 hours before reattesting to our contract, and a quick attestor as someone who does not. 

With this simple split, we can see the patient attestor increase their score by almost .5 and the quick attestor almost 0! Almost half of the patient attestors increased their score! With 2,700 reattesting after 12 hours, and half getting a higher score - this tool has driven some real traffic to new protocols!

Did our fun on-chain scoring tool inadvertently convince thousands of people to start acting like conscientious blockchain users? 

## User Type

```{r, warning = FALSE, message = FALSE}

User_type_query <- {
  "
               with base as (
                 select *,
                 regexp_substr_all(SUBSTR(DATA, 3, len(DATA)), '.{64}') AS segmented_data
                 from optimism.core.fact_event_logs
                 where block_timestamp > '2022-12-14'
                 and block_timestamp < '2023-01-31'
                 and contract_address = '0xee36eaad94d1cc1d0eccadb55c38bffb6be06c77' 
                 and topics[0]::string = '0x28710dfecab43d1e29e02aa56b2e1e610c0bae19135c9cf7a83a1adb6df96d85'
               ),
               decoded_data as (
                 select
                 block_number,
                 block_timestamp,
                 tx_hash,
                 origin_from_address,
                 origin_to_address,
                 event_index,
                 CONCAT('0x', SUBSTR(topics [1] :: STRING, 27, 40)) AS creator,
                 CONCAT('0x', SUBSTR(topics [2] :: STRING, 27, 40)) AS about,
                 replace(topics [3] :: STRING,'0x','') as key,
                 try_hex_decode_string(key::string) as decoded_key,
                 substr(data::string,131,(ethereum.public.udf_hex_to_int(segmented_data[1]::string) * 2)) as val,
                 try_hex_decode_string(val::string) as val_text
                 from base
               ),
               base_duplicates as (
                 select
                 distinct 
                 block_timestamp,
                 about as address,
                 origin_to_address,
                 val,
                 row_number() over (partition by about,origin_to_address order by block_timestamp asc) as attestation_number,
                 lag(block_timestamp,1) over (partition by about,origin_to_address order by block_timestamp asc) as date_diff,
                 lag(val,1) over (partition by about,origin_to_address order by block_timestamp asc) as val_diff
                 from decoded_data
                 where origin_to_address in ('0xd870a73a32d0b8c34ccf1e6098e9a26977cb605b')
               ),
               core_tab as (
               select 
               distinct
               a.address,
               case when datediff(minute,date_diff,block_timestamp) < 720 then 'Quick Attest'
               when datediff(minute,date_diff,block_timestamp) >= 720 then 'Patient Attest'
               else 'First Attestation'
               end as attestation_type,
               b.tag_name,
               c.ens_set,
               d.date_first
               from base_duplicates a
               left join (select distinct address, tag_name from crosschain.core.address_tags 
                  where blockchain= 'optimism'
                  and creator = 'flipside'
                  and tag_name = 'contract address') b
                  on a.address = b.address
               left join (select distinct owner as address, ens_set from crosschain.core.ez_ens where ENS_SET = 'Y') c
                  on a.address = c.address
              left join (select distinct from_address as address, min(block_timestamp) as date_first from OPTIMISM.CORE.FACT_TRANSACTIONS
                        where address in (select distinct address from base_duplicates)
                        group by 1) d
                  on a.address = d.address
               )
               select 
               attestation_type,
               sum(case when ens_set = 'Y' then 1 else 0 end)/count(distinct address)*100 as ens_set_percent,
               sum(case when tag_name is not null then 1 else 0 end)/ count(distinct address) * 100 as contract_address_percent,
               avg(datediff(day,date_first,CURRENT_DATE)) avg_days_since_first_tx
               from core_tab
               group by 1

  "
}
# not run 
# User_type_table <- auto_paginate_query(User_type_query, api_key = readLines("api_key.txt"))

# provided pre-ran 
User_type_table <- read.csv("User_type_table_data.csv")

```


```{r, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
# cat(reattestation_breakout_table) # output the table in a format good for HTML/PDF/docx conversion
colnames(User_type_table) = c('Attestation Type','ENS Set %', 'Contract Address %', 'Avg Days Since 1st Tx')
reactable(User_type_table[order(User_type_table[['ENS Set %']]),])
```


Breaking out our users into the 3 groups: we can see that those who patiently reattest seem to be more active on the chain! They have the highest percentage of ENS set, and a higher number of days since their first transaction than those who quickly reattest.

It is also an interesting call-out that we had 0 contract addresses attest to our tool - even on behalf of an EOA.

A simple scoring app that had no promise of any reward for a higher score - caused users to be more active and conscientious on Optimism; moreover, a simple split such as time between reattestations created a very clear delineation between user groups. Something as simple as an on-chain scoring app could segment users into 'good' users and 'bad' users. 


# Motivation

Looking at the users who used our Optimist Scored app, its clear that there has to be some underlying motivation to want to use and come back to it. Despite our hard work, its probably not because 'the app is super cool'. 

Looking at the big picture there are two reasons that stand out: Monetary reward and proof of action. 

The first, monetary reward, is a big attractor for all types of users, because who doesn't like free stuff? Granted, this attracts airdrop farmers, bots, etc. that may not be the best types of users. It also attracts new users to a protocol. If i gave an address the option between two similar protocols, were one had the potential to airdrop all historical users some tokens, and the other did not. Users would be more inclined to use the first protocol. 

In the case of our Attestation app, there was some circulation on twitter that the use of our scoring app would directly play a factor into the airdrop. While this isn't true, it motivated users to use the app, and some to return to the app with a higher score in hopes of a higher airdrop. 

The second, proof of action, is a very important factor - that i think is often under appreciated. Our attestation contract allowed users to attest to their score on chain. 
This means that there is proof that an address did certain actions, and elected to have their immortalized on chain. It is a bThis makes it easy for protocols to subset users based on scores - it also can help sybil detection algorythms to be more accurate with who is a bot and not. 

Doing something on chain is one thing, doing something on chain and having proof that you did it is another. 
# Conclusion

Overall, this was a very successful experiment around on-chain scoring tools. In the end it seems that rewarding users, either through reputation or monetary gain, encourages users to be more active on chain. However, there is something to be said about having a multi-categoried score available to a user. An NFT maxi who uses an app similar to this and sees a 0 in categories such as governance or defi, may be incentivised to participate in those for the sole purpose of their address not being associated with a 0 score. 

With these findings, we will continue to iterate on our scoring apps with ideas such as targeted recommendations for users, fun incentives, and direct goals. 

More fun coming soon <sup>tm</sup>